### 2009-02-03 articles/2009/geoinformatics/article.tex
text is done and handed in
git-svn-id: https://svn.osgeo.org/qgis/trunk@10100 c8812cc2-4d05-0410-92ff-de0c093fc19c

Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
background is Open Source GIS and applied remote sensing. 
\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been torturing computers and programming languages well over two decades. In 2002 he founded the Quantum GIS project. 
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>

@@

Quantum GIS project: \url{http://qgis.org}
\\QGIS Forum: \url{http://forum.qgis.org}
\\QGIS Blog: \url{http://blog.qgis.org}
\\QGIS User Mailing List:
\url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
\\QGIS IRC: Channel \#qgis port 6667 at \url{irc.freenode.net}
\\Open Source Geospatial Foundation: \url{http://www.osgeo.org}

>>>>

Otto Dassau <dassau@nature-consult.de>: Otto lives and works in Hannover,
Germany. His topics are FOSS GIS and applied remote sensing.
\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been
torturing computers and programming languages well over two decades. In 2002
he founded the Quantum GIS project. 
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in
Gauteng, South africa where he provides commercial support and development
services for QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in
Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich
and for his company that provides programming and consulting services for
FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works in Italy. He
heads a small and active group of professionals (biologists and agronomists)
under the name Faunalia.

@@

Quantum GIS project: \url{http://qgis.org}
\\QGIS Forum: \url{http://forum.qgis.org}
\\QGIS Blog: \url{http://blog.qgis.org}
\\QGIS User Mailing List: \url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
\\QGIS IRC: Channel \#qgis port 6667 at \url{irc.freenode.net}
\\Open Source Geospatial Foundation: \url{http://www.osgeo.org}
\\QGIS Map Server Project \url{http://karlinapp.ethz.ch/qgis\_wms}
\\GNU GPL: \url{http://www.fsf.org/licensing/licenses/gpl.html}
\\Open Source Geospatial Foundation: \url{http://www.osgeo.org}
